Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2015-09-17 LaTeX/supplemental.tex
setup biometrics style

\documentclass[11pt]{article}
\usepackage{amssymb, amsthm, amsmath}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}
\usepackage{bm}
\usepackage{verbatim}
\usepackage{lineno}
\usepackage{times}
\usepackage{soul}
\usepackage{color}
\usepackage{enumitem}
\usepackage{setspace}

@@

\usepackage[left=1in,top=1in,right=1in]{geometry}
\pdfpageheight 11in
\pdfpagewidth 8.5in
\linespread{2.0}
\input{mycommands.sty}

\begin{document}\linenumbers
\begin{center}
{\Large {\bf Supplemental material for A space-time skew-$t$ model for threshold exceedances}}\\

{\large Samuel A Morris\footnote[1]{North Carolina State University}, Brian J Reich\footnotemark[1]{}, Emeric Thibaud\footnote[2]{Colorado State University}, and Daniel Cooley\footnotemark[2]{}}

\today
\end{center}

\appendix
\section{Appendices}
\subsection{MCMC details} \label{a:mcmc}
The MCMC sampling for the model \ref{s:hier} is done using {\tt R} (http://www.r-project.org). Whenever possible, we select conjugate priors (see Appendix \ref{a:posterior}); however, for some of the parameters, no conjugate prior distributions exist.
For these parameters, we use a random walk Metropolis-Hastings update step.
In each Metropolis-Hastings update, we tune the algorithm during the burn-in period to give acceptance rates near 0.40.

\subsubsection*{Spatial knot locations}
For each day, we update the spatial knot locations, $\bw_1, \ldots, \bw_K$, using a Metropolis-Hastings block update.
Because the spatial domain is bounded, we generate candidate knots using the transformed knots $\bw^*_1, \ldots, \bw^*_K$ (see section \ref{s:temporal}) and a random walk bivariate Gaussian candidate distribution
\begin{align*}
	{\bw^*_k}^{(c)} \sim \text{N}({\bw^*_k}^{(r - 1)}, s^2 I_2)
\end{align*}
where ${\bw^*_k}^{(r - 1)}$ is the location for the transformed knot at MCMC iteration $r - 1$, $s$ is a tuning parameter, and $I_2$ is an identity matrix.
After candidates have been generated for all $K$ knots, the acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[ Y_t(\bs | \bw_1^{(c)}, \ldots, \bw_K^{(c)}, \ldots)] }{l[ Y_t(\bs | \bw_1^{(r - 1)}, \ldots, \bw_K^{(r - 1)}, \ldots)]} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K}\phi(\bw_k^{(c)})}{ \prod_{k = 1}^{K}\phi(\bw_k^{(r - 1)})} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K} p({\bw^*_k}^{(c)})}{ \prod_{k = 1}^{K} p({\bw^*_k}^{(r - 1)})}\right\}
\end{align*}
where $l$ is the likelihood given in (\ref{eq:hier}), and $p(\cdot)$ is the prior either taken from the time series given in (\ref{s:temporal}) or assumed to be uniform over $\calD$.
The candidate knots are accepted with probability $\min\{R, 1\}$.

\subsubsection*{Spatial random effects}
If there is no temporal dependence amongst the observations, we use a Gibbs update for $z_{tk}$, and the posterior distribution is given in \ref{a:posterior}.
If there is temporal dependence amongst the observations, then we update $z_{tk}$ using a Metropolis-Hastings update.
Because this model uses $|z_{tk}|$, we generate candidate random effects using the $z^*_{tk}$ (see Section \ref{s:temporal}) and a random walk Gaussian candidate distribution
\begin{align*}
  {z^*_{tk}}^{(c)} \sim \text{N}({z^*_{tk}}^{(r - 1)}, s^2)
\end{align*}
where ${z^*_{tk}}^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
The acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[Y_t(\bs) | z_{tk}^{(c)}, \ldots] }{ l[Y_t(\bs) | z_{tk}^{(r - 1)}]} \right\} \times \left\{ \frac{ p[ z_{tk}^{(c)} ] }{ p[ z_{tk}^{(r - 1)}]}\right\}
\end{align*}
where $p[\cdot]$ is the prior taken from the time series given in Section \ref{s:temporal}.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsubsection*{Variance terms}
When there is more than one site in a partition, then we update $\sigma^2_{tk}$ using a Metropolis-Hastings update.
First, we generate a candidate for $\sigma^2_{tk}$ using an IG$(a^*/s, b^*/s)$ candidate distribution in an independence Metropolis-Hastings update where $a^* = (n_{tk} + 1) / 2 + a$, $b^* = [Y_{tk}^T \Sigma^{-1}_{tk} Y_{tk} + z_{tk}^2] / 2 + b$, $n_{tk}$ is the number of sites in partition $k$ on day $t$, and $Y_{tk}$ and $\Sigma^{-1}_{tk}$ are the observations and precision matrix for partition $k$ on day $t$.
The acceptance ratio is
\begin{align*}
  R = \left\{
    \frac{ l[Y_t(\bs) | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[Y_t(\bs) | {\sigma^2_{tk}}^{(r - 1)}]}
    \right\} \times \left\{
    \frac{ l[z_{tk} | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[z_{tk} | {\sigma^2_{tk}}^{(r - 1)}, \ldots] }
    \right\} \times \left\{
    \frac{ p[ {\sigma^2_{tk}}^{(c)} ] }
         { p[ {\sigma^2_{tk}}^{(r - 1)}] }
    \right\} \times \left\{
    \frac{ c[ {\sigma^2_{tk}}^{(r - 1)}] }
         { c[ {\sigma^2_{tk}}^{(c)}]}
    \right\}
\end{align*}
where $p[\cdot]$ is the prior either taken from the time series given in Section \ref{s:temporal} or assumed to be IG$(a, b)$, and $c[\cdot]$ is the candidate distribution.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsubsection*{Spatial covariance parameters}
We update the three spatial covariance parameters, $\log(\rho)$, $\log(\nu)$, $\gamma$, using a Metropolis-Hastings block update step.
First, we generate a candidate using a random walk Gaussian candidate distribution
\begin{align*}
	\log(\rho)^{(c)} \sim \text{N}(\log(\rho)^{(r - 1)}, s^2)
\end{align*}
where $\log(\rho)^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
Candidates are generated for $\log(\nu)$ and $\gamma$ in a similar fashion.
The acceptance ratio is
\begin{align*}
	R = \left\{ \frac{ \prod_{t = 1}^{T} l[Y_t(\bs) | \rho^{(c)}, \nu^{(c)}, \gamma^{(c)}, \ldots] }{\prod_{t = 1}^{T} l[Y_t(\bs) | \rho^{(r-1)}, \nu^{(r-1)}, \gamma^{(r-1)}, \ldots] } \right\} \times \left\{ \frac{ p[\rho^{(c)}] }{ p[\rho^{(r - 1)] } } \right\} \times \left\{ \frac{ p[\nu^{(c)}] }{ p[\nu^{(r - 1)}] } \right\} \times \left\{ \frac{ p[ \gamma^{(c)} ] }{ p[\gamma^{(r - 1)} ] } \right\}.
\end{align*}
All three candidates are accepted with probability $\min\{R, 1\}$.

\subsection{Posterior distributions} \label{a:posterior}

\subsubsection*{Conditional posterior of $z_{tk} \mid \ldots $}\label{s:mvcondu}
If knots are independent over days, then the conditional posterior distribution of $|z_{tk}|$ is conjugate.
For simplicity, drop the subscript $t$, let $\tilde{z}_{tk} = |z_{tk}|$, and define
\begin{align*}
R(\bs) = \left\{
    \begin{array}{ll}
        Y(\bs) - X(\bs) \beta &s \in P_l\\[1em]
        Y(\bs) - X(\bs) \beta - \lambda \tilde{z}(\bs) \qquad & s \notin P_l
    \end{array}
\right.
\end{align*}
Let
\begin{align*}
    R_1 &= \text{the vector of } R(\bs) \text{ for } s \in P_l \\
    R_2 &= \text{the vector of } R(\bs) \text{ for } s \notin P_l \\
    \Omega &= \Sigma^{-1}.
\end{align*}
Then
\begin{align*}
    \pi(z_l | \ldots) &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)^T
        \left( \begin{array}{cc}
            \Omega_{11} & \Omega_{12}\\
            \Omega_{21} & \Omega_{22}
        \end{array} \right)
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)
        +  \frac{ {\tilde{z}_l}^2 }{ \sigma_l^2 }\right]
    \right\} I(z_l > 0) \\
        &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \Lambda_l {\tilde{z}_l}^2 - 2 \mu_l \tilde{z}_l \right] \right\}
\end{align*}
where
\begin{align*}
    \mu_l &= \lambda ( R_1^T \Omega_{11} + R_2^T \Omega_{21} )\bOne\\
    \Lambda_l &= \lambda^2 \bOne^T \Omega_{11} \bOne + \frac{ 1 }{ \sigma^2_l }.
\end{align*}
Then $\tilde{Z}_l | \ldots \sim N_{(0, \infty)} (\Lambda_l^{-1} \mu_l, \Lambda_l^{-1})$

@@

\subsection{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{a:proofsamepartition}
Consider a homogeneous spatial Poisson process with intensity $\mu$.
Define $A$ as the circle with center \hbox{$(\bs_1 + \bs_2) / 2$} and radius $h / 2$.
Then $\bs_1$ and $\bs_2$ are in different partitions almost surely if two or more points are in $A$.
Let $N(A)$ be the number of points in $A$, and let
\begin{align*}
  \mu(A) = \mu |A| = \mu \pi \left(\frac{h}{2}\right)^2 = \lambda h^2.
\end{align*}
Then
\begin{align*}
  P[N(A) \ge 2] &= 1 - P[N(A) = 0] - P[N(A) = 1]\\
                &= 1 - \exp\{-\lambda h^2\} - \lambda h^2 \exp\{-\lambda h^2\} \\
                &= 1 - (1 + \lambda h^2) \exp\{-\lambda h^2\}
\end{align*}
which goes to one as $h \rightarrow \infty$.

@@

\subsection{Skew-$t$ distribution} \label{a:skewt}
\subsubsection*{Univariate skew-$t$ distribution}
We say that $Y$ follows a univariate extended skew-$t$ distribution with location $\xi \in \calR$, scale $\omega > 0$, skew parameter $\alpha \in \calR$, and degrees of freedom $\nu$ if has distribution function
\begin{align}
  f_{\text{EST}}(y) = 2 f_T (z; \nu) F_T\left[ \alpha z \sqrt{ \frac{ \nu + 1 }{ \nu + z^2}}; \nu + 1 \right]
\end{align}
where $f_T(t; \nu)$ is a univariate Student's $t$ with $\nu$ degrees of freedom, $F_T(t; \nu) = P(T < t)$, and \hbox{$z = (y - \xi) / \omega$}.

@@

\subsubsection*{Extremal dependence}
For a bivariate skew-$t$ random variable $\bY = [Y(\bs), Y(\bt)]^T$, the $\chi(h)$ statistic \citep{Padoan2011} is given by
\begin{align} \label{eq:chiskew-t}
  \chi(h) = \bar{F}_{\text{EST}}\left\{ \frac{[x_1^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{\sqrt{1 - \varrho(h)^2}}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \frac{ [x_2^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{ \sqrt{1 - \varrho(h)^2} }; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\},
\end{align}
where $\bar{F}_{\text{EST}}$ is the univariate survival extended skew-$t$ function with zero location and unit scale, \hbox{$\varrho(h) = \text{cor}[y(\bs), y(\bt)]$}, $\alpha_j = \alpha_i \sqrt{1 - \varrho^2}$, $\tau_j = \sqrt{\eta + 1}(\alpha_j + \alpha_i \varrho)$, and $x_j = F_T(\bar{\alpha}_i \sqrt{\eta + 1}; 0, 1, \eta) / F_T(\bar{\alpha}_j \sqrt{\eta + 1}; 0, 1, \eta)$ with $j = 1, 2$ and $i = 2, 1$ and where $\bar{\alpha}_j = (\alpha_j + \alpha_i \varrho) / \sqrt{ 1 + \alpha_i^2 [1 - \varrho(h)^2]}$.

\subsubsection*{Proof that $\lim_{h \rightarrow \infty} \chi(h) > 0$}
Consider the bivariate distribution of $\bY = [Y(\bs), Y(\bt)]^T$, with $\varrho(h)$ given by (\ref{eq:matern}).
So, $\lim_{h \rightarrow \infty} \varrho(h) = 0$.
Then
\begin{align}
  \lim_{h \rightarrow \infty} \chi(h) = \bar{F}_{\text{EST}}\left\{ \sqrt{\eta + 1}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \sqrt{\eta + 1}; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\}.
\end{align}
Because the extended skew-$t$ distribution is not bounded above, for all $\bar{F}_{\text{EST}}(x) = 1 - F_{\text{EST} (x)} > 0$ for all $x < \infty$.
Therefore, for a skew-$t$ distribution, $\lim_{h \rightarrow \infty} \chi(h) > 0$.

\subsection{Simulation study pairwise difference results} \label{a:pdiffs}
The following tables show the methods that have significantly different Brier scores when using a Wilcoxon-Nemenyi-McDonald-Thompson test.
In each column, different letters signify that the methods have significantly different Brier scores.
For example, there is significant evidence to suggest that method 1 and method 4 have different Brier scores at $q(0.90)$, whereas there is not significant evidence to suggest that method 1 and method 2 have different Brier scores at $q(0.90)$.
In each table group A represents the group with the lowest Brier scores.
Groups are significant with a familywise error rate of $\alpha = 0.05$.

@@

% \begin{singlespace}
% \bibliographystyle{rss}
% \bibliography{library}
% \end{singlespace}

>>>>

% \documentclass[11pt]{article}
\documentclass[useAMS,usenatbib,referee]{biomweb}
% \usepackage{amssymb, amsthm, amsmath}
\usepackage{amssymb, amsmath}
\usepackage{bm}
\usepackage{graphicx}
% \usepackage[authoryear]{natbib}
\usepackage{bm}
\usepackage{verbatim}
\usepackage{lineno}
\usepackage{times}
\usepackage{soul}
\usepackage{color}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{appendix}
% \usepackage{caption}
% \captionsetup[table]{name=Web Table}

@@

% \usepackage[left=1in,top=1in,right=1in]{geometry}
% \pdfpageheight 11in
% \pdfpagewidth 8.5in
% \linespread{2.0}
\input{mycommands.sty}

\title[Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances]{Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley}
\author
{Samuel A Morris$^{1,*}$\email{samorris@ncsu.edu},
Brian J Reich$^{1}$,
Emeric Thibaud$^{2}$, and
Daniel Cooley$^{2}$\\
$^{1}$Department of Statistics, North Carolina State University, Raleigh, North Carolina, U.S.A. \\
$^{2}$Department of Statistics, Colorado State University, Fort Collins, Colorado, U.S.A.}

\begin{document} %\linenumbers
\maketitle
% \begin{center}
% {\Large {\bf Supplemental material for A space-time skew-$t$ model for threshold exceedances}}\\

% {\large Samuel A Morris\footnote[1]{North Carolina State University}, Brian J Reich\footnotemark[1]{}, Emeric Thibaud\footnote[2]{Colorado State University}, and Daniel Cooley\footnotemark[2]{}}

% \today
% \end{center}

% \appendix
\renewcommand{\thesection}{Web Appendix \Alph{section}}
% \renewcommand{\tablename}{Web Table}
% \renewcommand{\figurename}{Web Figure}
% \renewcommand{\thetable}{Web Table \arabic{table}}

\section{MCMC details} \label{a:mcmc}
The MCMC sampling for the model \ref{s:hier} is done using {\tt R} (http://www.r-project.org). Whenever possible, we select conjugate priors (see Appendix \ref{a:posterior}); however, for some of the parameters, no conjugate prior distributions exist.
For these parameters, we use a random walk Metropolis-Hastings update step.
In each Metropolis-Hastings update, we tune the algorithm during the burn-in period to give acceptance rates near 0.40.

\subsection*{Spatial knot locations}
For each day, we update the spatial knot locations, $\bw_1, \ldots, \bw_K$, using a Metropolis-Hastings block update.
Because the spatial domain is bounded, we generate candidate knots using the transformed knots $\bw^*_1, \ldots, \bw^*_K$ (see section \ref{s:temporal}) and a random walk bivariate Gaussian candidate distribution
\begin{align*}
	{\bw^*_k}^{(c)} \sim \text{N}({\bw^*_k}^{(r - 1)}, s^2 I_2)
\end{align*}
where ${\bw^*_k}^{(r - 1)}$ is the location for the transformed knot at MCMC iteration $r - 1$, $s$ is a tuning parameter, and $I_2$ is an identity matrix.
After candidates have been generated for all $K$ knots, the acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[ Y_t(\bs | \bw_1^{(c)}, \ldots, \bw_K^{(c)}, \ldots)] }{l[ Y_t(\bs | \bw_1^{(r - 1)}, \ldots, \bw_K^{(r - 1)}, \ldots)]} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K}\phi(\bw_k^{(c)})}{ \prod_{k = 1}^{K}\phi(\bw_k^{(r - 1)})} \right\} \times \left\{ \frac{ \prod_{k = 1}^{K} p({\bw^*_k}^{(c)})}{ \prod_{k = 1}^{K} p({\bw^*_k}^{(r - 1)})}\right\}
\end{align*}
where $l$ is the likelihood given in (\ref{eq:hier}), and $p(\cdot)$ is the prior either taken from the time series given in (\ref{s:temporal}) or assumed to be uniform over $\calD$.
The candidate knots are accepted with probability $\min\{R, 1\}$.

\subsection*{Spatial random effects}
If there is no temporal dependence amongst the observations, we use a Gibbs update for $z_{tk}$, and the posterior distribution is given in \ref{a:posterior}.
If there is temporal dependence amongst the observations, then we update $z_{tk}$ using a Metropolis-Hastings update.
Because this model uses $|z_{tk}|$, we generate candidate random effects using the $z^*_{tk}$ (see Section \ref{s:temporal}) and a random walk Gaussian candidate distribution
\begin{align*}
  {z^*_{tk}}^{(c)} \sim \text{N}({z^*_{tk}}^{(r - 1)}, s^2)
\end{align*}
where ${z^*_{tk}}^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
The acceptance ratio is
\begin{align*}
  R = \left\{ \frac{ l[Y_t(\bs) | z_{tk}^{(c)}, \ldots] }{ l[Y_t(\bs) | z_{tk}^{(r - 1)}]} \right\} \times \left\{ \frac{ p[ z_{tk}^{(c)} ] }{ p[ z_{tk}^{(r - 1)}]}\right\}
\end{align*}
where $p[\cdot]$ is the prior taken from the time series given in Section \ref{s:temporal}.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsection*{Variance terms}
When there is more than one site in a partition, then we update $\sigma^2_{tk}$ using a Metropolis-Hastings update.
First, we generate a candidate for $\sigma^2_{tk}$ using an IG$(a^*/s, b^*/s)$ candidate distribution in an independence Metropolis-Hastings update where $a^* = (n_{tk} + 1) / 2 + a$, $b^* = [Y_{tk}^T \Sigma^{-1}_{tk} Y_{tk} + z_{tk}^2] / 2 + b$, $n_{tk}$ is the number of sites in partition $k$ on day $t$, and $Y_{tk}$ and $\Sigma^{-1}_{tk}$ are the observations and precision matrix for partition $k$ on day $t$.
The acceptance ratio is
\begin{align*}
  R = \left\{
    \frac{ l[Y_t(\bs) | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[Y_t(\bs) | {\sigma^2_{tk}}^{(r - 1)}]}
    \right\} \times \left\{
    \frac{ l[z_{tk} | {\sigma^2_{tk}}^{(c)}, \ldots] }
         { l[z_{tk} | {\sigma^2_{tk}}^{(r - 1)}, \ldots] }
    \right\} \times \left\{
    \frac{ p[ {\sigma^2_{tk}}^{(c)} ] }
         { p[ {\sigma^2_{tk}}^{(r - 1)}] }
    \right\} \times \left\{
    \frac{ c[ {\sigma^2_{tk}}^{(r - 1)}] }
         { c[ {\sigma^2_{tk}}^{(c)}]}
    \right\}
\end{align*}
where $p[\cdot]$ is the prior either taken from the time series given in Section \ref{s:temporal} or assumed to be IG$(a, b)$, and $c[\cdot]$ is the candidate distribution.
The candidate is accepted with probability $\min\{R, 1\}$.

\subsection*{Spatial covariance parameters}
We update the three spatial covariance parameters, $\log(\rho)$, $\log(\nu)$, $\gamma$, using a Metropolis-Hastings block update step.
First, we generate a candidate using a random walk Gaussian candidate distribution
\begin{align*}
	\log(\rho)^{(c)} \sim \text{N}(\log(\rho)^{(r - 1)}, s^2)
\end{align*}
where $\log(\rho)^{(r-1)}$ is the value at MCMC iteration $r - 1$, and $s$ is a tuning parameter.
Candidates are generated for $\log(\nu)$ and $\gamma$ in a similar fashion.
The acceptance ratio is
\begin{align*}
	R = \left\{ \frac{ \prod_{t = 1}^{T} l[Y_t(\bs) | \rho^{(c)}, \nu^{(c)}, \gamma^{(c)}, \ldots] }{\prod_{t = 1}^{T} l[Y_t(\bs) | \rho^{(r-1)}, \nu^{(r-1)}, \gamma^{(r-1)}, \ldots] } \right\} \times \left\{ \frac{ p[\rho^{(c)}] }{ p[\rho^{(r - 1)] } } \right\} \times \left\{ \frac{ p[\nu^{(c)}] }{ p[\nu^{(r - 1)}] } \right\} \times \left\{ \frac{ p[ \gamma^{(c)} ] }{ p[\gamma^{(r - 1)} ] } \right\}.
\end{align*}
All three candidates are accepted with probability $\min\{R, 1\}$.

\section{Posterior distributions} \label{a:posterior}

\subsection*{Conditional posterior of $z_{tk} \mid \ldots $}\label{s:mvcondu}
If knots are independent over days, then the conditional posterior distribution of $|z_{tk}|$ is conjugate.
For simplicity, drop the subscript $t$, let $\tilde{z}_{tk} = |z_{tk}|$, and define
\begin{align*}
R(\bs) = \left\{
    \begin{array}{ll}
        Y(\bs) - X(\bs) \beta &s \in P_l\\[1em]
        Y(\bs) - X(\bs) \beta - \lambda \tilde{z}(\bs) \qquad & s \notin P_l
    \end{array}
\right.
\end{align*}
Let
\begin{align*}
    R_1 &= \text{the vector of } R(\bs) \text{ for } s \in P_l \\
    R_2 &= \text{the vector of } R(\bs) \text{ for } s \notin P_l \\
    \Omega &= \Sigma^{-1}.
\end{align*}
Then
\begin{align*}
    \pi(z_l | \ldots) &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)^T
        \left( \begin{array}{cc}
            \Omega_{11} & \Omega_{12}\\
            \Omega_{21} & \Omega_{22}
        \end{array} \right)
        \left( \begin{array}{c}
            R_1 - \lambda \tilde{z}_l \bOne\\
            R_2
        \end{array} \right)
        +  \frac{ {\tilde{z}_l}^2 }{ \sigma_l^2 }\right]
    \right\} I(z_l > 0) \\
        &\propto \exp \left\{ -\frac{ 1 }{ 2 } \left[ \Lambda_l {\tilde{z}_l}^2 - 2 \mu_l \tilde{z}_l \right] \right\}
\end{align*}
where
\begin{align*}
    \mu_l &= \lambda ( R_1^T \Omega_{11} + R_2^T \Omega_{21} )\bOne\\
    \Lambda_l &= \lambda^2 \bOne^T \Omega_{11} \bOne + \frac{ 1 }{ \sigma^2_l }.
\end{align*}
Then $\tilde{Z}_l | \ldots \sim N_{(0, \infty)} (\Lambda_l^{-1} \mu_l, \Lambda_l^{-1})$

@@

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{a:proofsamepartition}
Consider a homogeneous spatial Poisson process with intensity $\mu$.
Define $A$ as the circle with center \hbox{$(\bs_1 + \bs_2) / 2$} and radius $h / 2$.
Then $\bs_1$ and $\bs_2$ are in different partitions almost surely if two or more points are in $A$.
Let $N(A)$ be the number of points in $A$, and let
\begin{align*}
  \mu(A) = \mu |A| = \mu \pi \left(\frac{h}{2}\right)^2 = \lambda h^2.
\end{align*}
Then
\begin{align*}
  P[N(A) \ge 2] &= 1 - P[N(A) = 0] - P[N(A) = 1]\\
                &= 1 - \exp\{-\lambda h^2\} - \lambda h^2 \exp\{-\lambda h^2\} \\
                &= 1 - (1 + \lambda h^2) \exp\{-\lambda h^2\}
\end{align*}
which goes to one as $h \rightarrow \infty$.

@@

\section{Skew-$t$ distribution} \label{a:skewt}
\subsection*{Univariate skew-$t$ distribution}
We say that $Y$ follows a univariate extended skew-$t$ distribution with location $\xi \in \calR$, scale $\omega > 0$, skew parameter $\alpha \in \calR$, and degrees of freedom $\nu$ if has distribution function
\begin{align}
  f_{\text{EST}}(y) = 2 f_T (z; \nu) F_T\left[ \alpha z \sqrt{ \frac{ \nu + 1 }{ \nu + z^2}}; \nu + 1 \right]
\end{align}
where $f_T(t; \nu)$ is a univariate Student's $t$ with $\nu$ degrees of freedom, $F_T(t; \nu) = P(T < t)$, and \hbox{$z = (y - \xi) / \omega$}.

@@

\subsection*{Extremal dependence}
For a bivariate skew-$t$ random variable $\bY = [Y(\bs), Y(\bt)]^T$, the $\chi(h)$ statistic \citep{Padoan2011} is given by
\begin{align} \label{eq:chiskew-t}
  \chi(h) = \bar{F}_{\text{EST}}\left\{ \frac{[x_1^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{\sqrt{1 - \varrho(h)^2}}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \frac{ [x_2^{1 / \eta} - \varrho(h)] \sqrt{\eta + 1} }{ \sqrt{1 - \varrho(h)^2} }; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\},
\end{align}
where $\bar{F}_{\text{EST}}$ is the univariate survival extended skew-$t$ function with zero location and unit scale, \hbox{$\varrho(h) = \text{cor}[y(\bs), y(\bt)]$}, $\alpha_j = \alpha_i \sqrt{1 - \varrho^2}$, $\tau_j = \sqrt{\eta + 1}(\alpha_j + \alpha_i \varrho)$, and $x_j = F_T(\bar{\alpha}_i \sqrt{\eta + 1}; 0, 1, \eta) / F_T(\bar{\alpha}_j \sqrt{\eta + 1}; 0, 1, \eta)$ with $j = 1, 2$ and $i = 2, 1$ and where $\bar{\alpha}_j = (\alpha_j + \alpha_i \varrho) / \sqrt{ 1 + \alpha_i^2 [1 - \varrho(h)^2]}$.

\subsection*{Proof that $\lim_{h \rightarrow \infty} \chi(h) > 0$}
Consider the bivariate distribution of $\bY = [Y(\bs), Y(\bt)]^T$, with $\varrho(h)$ given by (\ref{eq:matern}).
So, $\lim_{h \rightarrow \infty} \varrho(h) = 0$.
Then
\begin{align}
  \lim_{h \rightarrow \infty} \chi(h) = \bar{F}_{\text{EST}}\left\{ \sqrt{\eta + 1}; 0, 1, \alpha_1, \tau_1, \eta + 1 \right\} + \bar{F}_{\text{EST}}\left\{ \sqrt{\eta + 1}; 0, 1, \alpha_2, \tau_2, \eta + 1 \right\}.
\end{align}
Because the extended skew-$t$ distribution is not bounded above, for all $\bar{F}_{\text{EST}}(x) = 1 - F_{\text{EST} (x)} > 0$ for all $x < \infty$.
Therefore, for a skew-$t$ distribution, $\lim_{h \rightarrow \infty} \chi(h) > 0$.

\section{Simulation study pairwise difference results} \label{a:pdiffs}
The following tables show the methods that have significantly different Brier scores when using a Wilcoxon-Nemenyi-McDonald-Thompson test.
In each column, different letters signify that the methods have significantly different Brier scores.
For example, there is significant evidence to suggest that method 1 and method 4 have different Brier scores at $q(0.90)$, whereas there is not significant evidence to suggest that method 1 and method 2 have different Brier scores at $q(0.90)$.
In each table group A represents the group with the lowest Brier scores.
Groups are significant with a familywise error rate of $\alpha = 0.05$.

@@

% \begin{singlespace}
\bibliographystyle{biom}
\bibliography{library}
% \end{singlespace}
